---
title: "From gprofiler2 to Cytoscape network"
author: Astrid Deschênes and Pascal Belleau
output:
  BiocStyle::html_document:
    toc: true
bibliography: gprofiler2cytoscape.bibtex
vignette: >
  %\VignetteIndexEntry{From gprofiler2 to Cytoscape network}
  %\VignettePackage{gprofiler2cytoscape}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r style, echo = FALSE, results = 'hide', warning=FALSE, message=FALSE}
BiocStyle::markdown()

suppressPackageStartupMessages({
  library(knitr)
  library(gprofiler2cytoscape)
})

set.seed(1214)
```

<br />
**Package**: `r Rpackage("gprofiler2cytoscape")`<br />
**Authors**: `r packageDescription("gprofiler2cytoscape")[["Author"]]`<br />
**Version**: `r packageDescription("gprofiler2cytoscape")$Version`<br />
**Compiled date**: `r Sys.Date()`<br />
**License**: `r packageDescription("gprofiler2cytoscape")[["License"]]`<br />


# Licensing 

The `r Githubpkg("adeschen/gprofiler2cytoscape")` package and the underlying 
`r Githubpkg("adeschen/gprofiler2cytoscape")` code are distributed under the 
Artistic license 2.0. You are free to use and redistribute this software. 

# Introduction

TODO


# Session info

Here is the output of sessionInfo() on the system on which this document 
was compiled:

```{r sessionInfo, echo=FALSE}
sessionInfo()
```


# References


